---
title: "DATA 606 Data Project Proposal"
author: "Weijian Cai"
date: "March 31, 2019"
output: html_document
---
### Data Preparation

```{r setup, echo=TRUE,results='hide', warning=FALSE, message=FALSE}
# load data
library(DT)
df <- read.csv("https://raw.githubusercontent.com/Weicaidata/606/master/bad-drivers.csv")
```

```{r}
summary(df)
datatable(df)
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**  
Which State Has The Worst Drivers?


### Cases 

**What are the cases, and how many are there?**  
```{r}
nrow(df)
```
cases are each individual states of U.S.



### Data collection 

**Describe the method of data collection.**
The dataset is collected by national highway trafic safety administration.



### Type of study 

**What type of study is this (observational/experiment)?**
It is observational study.



### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**
https://raw.githubusercontent.com/fivethirtyeight/data/master/bad-drivers/bad-drivers.csv




### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**  
Number of drivers involved in fatal collisions is the response variable. It is quantitative.



### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**  
Each state is independent variable, it is qualitative.



### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.** 

```{r}
summary(df)
```

```{r}
barplot(df$Number.of.drivers.involved.in.fatal.collisions.per.billion.miles)
```
