---
title: "HW7_606"
author: "Weijian Cai"
date: "April 14, 2019"
output: html_document
---
###7.24Nutrition at Starbucks, Part I
####(a) Describe the relationship between number of calories and amount of carbohydrates (in grams) that Starbucks food menu items contain.

It is a positive relationship and appears to be linear regression.

####(b) In this scenario, what are the explanatory and response variables?
The explanatory variable is the number of calories, and the response variable is the number of carbs.

####(c) Why might we want to fit a regression line to these data?
we are able to  prefict the amount of carbohydrates based on calories.

####(d) Do these data meet the conditions required for fitting a least squares line?
Yes, since the residuals are normal and the histogram is symmetric.

###7.26 Body measurements, Part III. 
####(a) Write the equation of the regression line for predicting height
Yh= 105.967+0.608Xs

####(b) Interpret the slope and the intercept in this context.
The slope means that the height would increase 0.608 cm for every 1 cm increase of shoulder girth. The intercept means when shoulder girth is 0 cm, the height is 105.9651 cm.

####(c) Calculate R2 of the regression line for predicting height from shoulder girth, and interpret it in the context of the application.
```{r}
R=0.67
R2=R*R
R2
```

####(d) A randomly selected student from your class has a shoulder girth of 100 cm. Predict the height of this student using the model.
```{r}
x <- 100

r<- 0.608*x + 105.967
r
```

####(e) The student from part (d) is 160 cm tall. Calculate the residual, and explain what this residual means.
the residual is the difference between actual value minus the estimate
```{r}
Res=160 - 166.7545
Res
```

####(f) A one year old has a shoulder girth of 56 cm. Would it be appropriate to use this linear model to predict the height of this child?  
No, since is not within the range of this model.

###7.30 Cats, Part I
####(a) Write out the linear model.
y=-0.357+4.034x

####(b) Interpret the intercept.
when body weight equal 0, the heart weight will be -0.357g.

####(c) Interpret the slope.
For every 1 kg increases in body weight, the heart weight increase 4.034 g.

####d) Interpret R2.
64.66% of the variation in heart weight is explained by the other vaiable body weight.

####(e) Calculate the correlation coecient
```{r}
R2 <- 0.6466
r <- sqrt(R2)
r
```


###7.40 Rate my professor
####(a) Given that the average standardized beauty score is -0.0883 and average teaching evaluation score is 3.9983, calculate the slope. Alternatively, the slope may be computed using just the information provided in the model summary table
```{r}
b40 <- (3.9983 - 4.010)/-0.0883
b40
```


####(b) Do these data provide convincing evidence that the slope of the relationship between teaching evaluation and beauty is positive? Explain your reasoning.
The p-value equals 0, which is less than the alpha level 0.05. Then we have sufficient evidence to reject the null hypothesis.

####(c) List the conditions required for linear regression and check if each one is satisfied for this model based on the following diagnostic plots.
the histogram of the residuals shows a symmetric and unimodal shape.

