---
title: "HW_C5_606"
author: "Weijian Cai"
date: "March 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##5.6 Working backwards, Part II
```{r}
sa_mean <- ((77+65)/2)
sa_mean
```

```{r}
moe1 <- ((77-65)/2)
moe1
```
standard devation =17.53481
```{r}
tvalue<- qt(.95,(25-1))
sd<- (moe1/tvalue)*5
sd
```


##5.14 SAT scores
###(a) Raina wants to use a 90% confidence interval. How large a sample should she collect?
```{r}
moe <- 25
sd <- 250
z <- qnorm(0.95)
n <- ((z * sd)/ moe)^2
n
```

####b) Luke wants to use a 99% confidence interval. Without calculating the actual sample size, determine whether his sample should be larger or smaller than Raina's, and explain your reasoning.  
Luke's sample size should be larger, since it has a larger z score.  

####(c) Calculate the minimum required sample size for Luke.
the miimum is 666.
```{r}
moe = 25
sd = 250
z = 2.58
n = ((sd*z)/moe)^2
n
```


###5.20 High School and Beyond, Part I. T
####(a) Is there a clear di???erence in the average reading and writing scores?
No, there is no clear difference.  

#### b) Are the reading and writing scores of each student independent of each other?
Yes, they are.

#### c) Create hypotheses appropriate for the following research question: is there an evident difference in the average score of students in the reading and writing exam?
Ho: there are no differece between the average score in reading and writing.
Ha: there are difference betwwen the average score in reading and writing.

####(d) Check the conditions required to complete this test
It is  independent and normal distribution, sample size is less than 10%.

####(e)
since the p value is more than 0.05, we can not reject the null hypothesis.
```{r}
mean_diff <- -0.545
sd <- 8.887
n <- 200
se <- sd / sqrt(n)
t <- (mean_diff - 0)/ se
p <- pt(t, n-1)
p
```


####(f) What type of error might we have made? Explain what the error means in the context of the application
type 2

#### g) Based on the results of this hypothesis test, would you expect a confidence interval for the average difference between the reading and writing scores to include 0? Explain your reasoning.
Yes, since the HO hypothesis we fail to reject.

### 5.32 Fuel efficiency of manual and automatic cares, Part I
Ho: there is no difference between automatic and manual car
Ha: there is difference between automatic and manual car

We can reject the Ho hyothesis, since the p value is less than 0.05.
```{r}
n <- 26
mean_diff <- 16.12 - 19.85
se_diff <- sqrt((3.58^2/n)+(4.51^2/n))
t1 <- (mean_diff - 0)/ se_diff
P <- pt(t1, n-1)
P
```

###5.48 Work hours and education.
####(a) Write hypotheses for evaluating whether the average number of hours worked varies across the five groups.
Ho: Average number of hours worked among all five groups are equal.  
Ha: Avergae number of hours worked among all five groups are not equal.  

#### b) Check conditions and describe any assumptions you must make to proceed with the test. 
The observations are independent and approximately normal.

#### c) Below is part of the output associated with this test. Fill in the empty cells.  
|         |Df   | Sum Sq  |Mean Sq| F value  | Pr (>F) |
|---------|-----|---------|-------|----------|---------|
|degree   | **4**    |  **2004.1** | 501.54  | **2.186745** | 0.0682 |
|Residuals| **1167** |  267382| **229.12**   |              |
|Total    | **1171** | **269386.1** |        |              |

###(d) What is the conclusion of the test?
since the p value = 0.0682, which is greater than 0.05, w fail to reject the HO hypothesis.



