---
title: "lab000"
author: "Weijian Cai"
date: "February 5, 2019"
output: html_document
---

```{r load-abrbuthnot-data, eval=TRUE}
source("more/arbuthnot.R")
```

1.  What command would you use to extract just the counts of girls baptized? Try
```{r}
arbuthnot$girls
```
 
2.  Is there an apparent trend in the number of girls baptized over the years?    How would you describe it?

## since 1660, the number of girls have been increased gradually. 


3.  Now, make a plot of the proportion of boys over time. What do you see? 

##The ratio is greater than 0.5 all along years , that means there were more new born boys than girls.
```{r}
plot(arbuthnot$year, arbuthnot$boys / (arbuthnot$boys + arbuthnot$girls), type = "l")
```


## On Your Own

In the previous few pages, you recreated some of the displays and preliminary 
analysis of Arbuthnot's baptism data. Your assignment involves repeating these 
steps, but for present day birth records in the United States.  Load up the 
present day data with the following command.

```{r load-present-data, eval=TRUE}
source("more/present.R")
```

The data are stored in a data frame called `present`.

-   What years are included in this data set? What are the dimensions of the 
    data frame and what are the variable or column names?
##years included in the data set
```{r}
present$year
```
##dimension of the data frame
```{R}
dim(present)
```

##column name
```{r}
names(present)
```

-   How do these counts compare to Arbuthnot's? Are they on a similar scale?

##the present data set have much larger new born compare to Arbuthnot's.
```{r}
summary(present)
summary(arbuthnot)
```

-   Make a plot that displays the boy-to-girl ratio for every year in the data 
    set. What do you see? Does Arbuthnot's observation about boys being born in
    greater proportion than girls hold up in the U.S.? Include the plot in your 
    response.

##plot displays the boy-to-girl ration of present data set.It shows that the ratio were always greater than 1, and the trend was downhill.
```{r}
plot(x=present$year, y=present$boys/present$girls)
```

-   In what year did we see the most total number of births in the U.S.? You can

```{R}
present$total=present$boys + present$girls
which.max(present$total)
present[22, ]
```
